Using SMT engine to generate Symbolic Automata\thanks{This work was partially funded by the Associated Team FM4CPS between INRIA and ECNU, Shanghai}

### 2017-04-20 2017-Xudong-SMT/submit-ICTAC2017.tex
Change the font style of variables.
Add two new commands \OTvar and \OTland.

%\usepackage{amsfonts}
%\usepackage{fancyhdr}
%\usepackage{cite}
%\usepackage{ifthen}
%\usepackage{amssymb}
%\usepackage{fancyhdr}
%\usepackage{pifont}
\usepackage{stmaryrd}
\usepackage{mathtools,mathpartir}
\usepackage{proof}
%\usepackage{setspace}
%\usepackage{indentfirst}
\usepackage{amsmath,amssymb,amscd,mathrsfs}
\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}
\usepackage{epsfig,color,subfigure,enumitem}
\newcommand{\TODO}[1]{\textcolor{red}{\textbf{[TODO:#1]}}}
\newcommand{\NOTE}[1]{\textcolor{blue}{\textbf{[NOTE:#1]}}}
\newcommand{\ERIC}[1]{\textcolor{blue}{#1}}
\definecolor{airforceblue}{rgb}{0.26, 0.44, 0.56}
\newcommand{\QIN}[1]{\textcolor{airforceblue}{#1}}
\newcommand{\coloncolon}{{:\hspace{-.2ex}:}}
\makeatletter
\newcommand{\raisemath}[1]{\mathpalette{\raisem@th{#1}}}
\newcommand{\raisem@th}[3]{\raisebox{#1}{$#2#3$}}
\makeatother

@@

\paragraph{Sorts}
\QIN{
Sorts are represented by a given name, showing the ownership of the variables and constants. The
sort of actions is built by the constant actions. There \emph{must} be one sort for actions, and eventually
several others for the types of data parameters. In the LOTOS example, we have the $Action$ sort:
}
\[ Action = \{ l, \delta, r, p, q, acc \} \]

@@

 \[VOID: \quad  < Action, Int > \rightarrow Action . \]

@@

\begin{figure}[t]
%$\begin{array}{@{}r@{}l@{}}
%%{s0---a-->s1},   {---:hb:15:2-->},   (:ra:15:2 = act:sva:1:3)/\(:ra:152:1 = l)/\(a = :ra:152:1)/\(l!= a)/\(:hb:15:2 = y:sva:15:2)/\(:ra:15:2 = y:sva:15:2)/\(y:sva:15:2 != l)/\(:ra:1:3 = act:sva:1:3)
%    ot  = &\openrule{\{0 \xrightarrow{a} 1\}, ~~\{\xrightarrow{:hb:15:2}\}, ~~:ra:15:2=act:sva:1:3 \\
%    \!\land\!:ra:152:1=l \!\land\! a=:ra:152:1 \!\land\! a \neq l \!\land\! :hb:15:2 = y:sva:15:2 \\
%    \!\land\! :ra:15:2 = y:sva:15:2  \!\land\! y:sva:15:2 \neq l \!\land\! :ra:1:3 = act:sva:1:3}
%    {\ostate{00} \xrightarrow{:ra:1:3} \ostate{10}}\\
%  \end{array}$
%\caption{One of the unsatisfiable open transitions in CCS running example}  \label{schema:unsat-ot}
%\end{figure}

%{s0---delta-->s0},   {---:hb_P:12:1-->},   (:ra:11:1=l)/\(delta=:ra:11:1)/\(var_s0=0)/\(:hb_P:12:1=a1:sva_SV0:1:1)/\(:ra:1:1=a1:sva_SV0:1:1)/\(a1:sva_SV0:1:1!=delta(x)),   {var_s0 := 1}
$\begin{array}{@{}r@{}l@{}}
    ot  = &\openrule{\{0 \xrightarrow{\delta} 0\}, ~~\{\xrightarrow{:hb:12:1}\}, ~~:ra:11:1=l \!\land\! \delta=:ra:11:1 \!\land\! s0=0 \\
     \!\land\! \texttt{:hb:12:1}=\texttt{a1:sva:1:1} \!\land\! :ra:1:1=a1:sva:1:1 \!\land\! a1:sva:1:1 \neq \delta(x), ~~\{s0 \leftarrow 1\}}
    {\ostate{00} \xrightarrow{:ra:1:1} \ostate{00}}\\
  \end{array}$
\caption{One of the unsatisfiable open transitions in LOTOS running example}  \label{schema:unsat-ot}
\end{figure}

@@

\[(VOID\ (action3\ Action)(data\ Int)) .\]

@@

\[(declare\text{-}fun\ VOID\ (Action\ Int)\ Action) .\]
%Although in Fig~\ref{schema:smt-lib} we have not declared $functions$ outside of $datatypes$, there still exists $functions$ declared independently. The input and output types of the $function$ are also determined by the construct of the  $operators$ in the presentation. For example, we define a new operator to present the equation between two actions in LOTOS example $\text{EQUAL}$ in the format likes:
%
%\[EQUAL: \quad < Action , Action > \rightarrow Bool .\]
%
%It will be translated into the Z3 statement: 
%
%\[\text{(declare-fun\ EQUAL\ (Action\ Action)\ Bool) .}\]

@@

\[\text{(declare-const\ |:ra:1:1|\ Action) .}\]

@@

\[(:ra:11:1=l)\land(delta=:ra:11:1) .\]

@@

\[(assert\ (=\ |:ra:11:1|\ l))\ \ \ (assert\ (=\ delta\ |:ra:11:1|))\]

>>>>

%\usepackage{amsfonts}
%\usepackage{fancyhdr}
%\usepackage{cite}
%\usepackage{ifthen}
%\usepackage{amssymb}
%\usepackage{fancyhdr}
%\usepackage{pifont}
\usepackage{stmaryrd}
\usepackage{mathtools,mathpartir}
\usepackage{proof}
%\usepackage{setspace}
%\usepackage{indentfirst}
\usepackage{amsmath,amssymb,amscd,mathrsfs}
\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}
\usepackage{epsfig,color,subfigure,enumitem}
\newcommand{\TODO}[1]{\textcolor{red}{\textbf{[TODO:#1]}}}
\newcommand{\NOTE}[1]{\textcolor{blue}{\textbf{[NOTE:#1]}}}
\newcommand{\ERIC}[1]{\textcolor{blue}{#1}}
\newcommand{\OTvar}{\texttt}
\newcommand{\OTland}{\ \land\ }
\definecolor{airforceblue}{rgb}{0.26, 0.44, 0.56}
\newcommand{\QIN}[1]{\textcolor{airforceblue}{#1}}
\newcommand{\coloncolon}{{:\hspace{-.2ex}:}}
\makeatletter
\newcommand{\raisemath}[1]{\mathpalette{\raisem@th{#1}}}
\newcommand{\raisem@th}[3]{\raisebox{#1}{$#2#3$}}
\makeatother

@@

\paragraph{Sorts}
\QIN{
Sorts are represented by a given name, showing the ownership of the variables and constants. The
sort of actions is built by the constant actions. There \emph{must} be one sort for actions, and eventually
several others for the types of data parameters. In the LOTOS example, we have the $Action$ sort:
}
\[\OTvar{Action = } \{ l, \delta, r, p, q, acc \} .\]

@@

 \[\OTvar{VOID:}\OTvar{< Action, Int >} \rightarrow \OTvar{Action .} \]

@@

\begin{figure}[t]
%$\begin{array}{@{}r@{}l@{}}
%%{s0---a-->s1},   {---:hb:15:2-->},   (:ra:15:2 = act:sva:1:3)/\(:ra:152:1 = l)/\(a = :ra:152:1)/\(l!= a)/\(:hb:15:2 = y:sva:15:2)/\(:ra:15:2 = y:sva:15:2)/\(y:sva:15:2 != l)/\(:ra:1:3 = act:sva:1:3)
%    ot  = &\openrule{\{0 \xrightarrow{a} 1\}, ~~\{\xrightarrow{:hb:15:2}\}, ~~:ra:15:2=act:sva:1:3 \\
%    \OTland:ra:152:1=l \OTland a=:ra:152:1 \OTland a \neq l \OTland :hb:15:2 = y:sva:15:2 \\
%    \OTland :ra:15:2 = y:sva:15:2  \OTland y:sva:15:2 \neq l \OTland :ra:1:3 = act:sva:1:3}
%    {\ostate{00} \xrightarrow{:ra:1:3} \ostate{10}}\\
%  \end{array}$
%\caption{One of the unsatisfiable open transitions in CCS running example}  \label{schema:unsat-ot}
%\end{figure}

%{s0---delta-->s0},   {---:hb_P:12:1-->},   (:ra:11:1=l)/\(delta=:ra:11:1)/\(var_s0=0)/\(:hb_P:12:1=a1:sva_SV0:1:1)/\(:ra:1:1=a1:sva_SV0:1:1)/\(a1:sva_SV0:1:1!=delta(x)),   {var_s0 := 1}
$\begin{array}{@{}r@{}l@{}}
    ot  = &\openrule{\{0 \xrightarrow{\delta} 0\}, ~~\{\xrightarrow{:hb:12:1}\}, ~~\OTvar{:ra:11:1}=l \OTland \delta=\OTvar{:ra:11:1} \OTland \OTvar{s0}=0 \\
     \OTland \OTvar{:hb:12:1}=\OTvar{a1:sva:1:1} \OTland \OTvar{:ra:1:1}=\OTvar{a1:sva:1:1} \OTland \OTvar{a1:sva:1:1} \neq \delta(x), ~~\{\OTvar{s0} \leftarrow 1\}}
    {\ostate{00} \xrightarrow{\OTvar{:ra:1:1}} \ostate{00}}\\
  \end{array}$
\caption{One of the unsatisfiable open transitions in LOTOS running example}  \label{schema:unsat-ot}
\end{figure}

@@

\[\OTvar{(VOID\ (action3\ Action)(data\ Int)) .}\]

@@

\[\OTvar{(declare\text{-}fun\ VOID\ (Action\ Int)\ Action) .}\]
%Although in Fig~\ref{schema:smt-lib} we have not declared $functions$ outside of $datatypes$, there still exists $functions$ declared independently. The input and output types of the $function$ are also determined by the construct of the  $operators$ in the presentation. For example, we define a new operator to present the equation between two actions in LOTOS example $\text{EQUAL}$ in the format likes:
%
%\[EQUAL: \quad < Action , Action > \rightarrow Bool .\]
%
%It will be translated into the Z3 statement: 
%
%\[\text{(declare-fun\ EQUAL\ (Action\ Action)\ Bool) .}\]

@@

\[\OTvar{(declare-const\ |:ra:1:1|\ Action) .}\]

@@

\[\OTvar{(:ra:11:1=l)} \OTland \OTvar{(delta=:ra:11:1) .}\]

@@

\[\OTvar{(assert\ (=\ |:ra:11:1|\ l))\ \ \ (assert\ (=\ delta\ |:ra:11:1|)) .}\]
